Supplement A: Estimating Travel Cost

### 2024-02-26 R/least-cost-paths.qmd
add 80 character linebreaks to qmd

<!-- 
RStudio/Quarto is having some issues with figure sizing, 
so using this hacky CSS solution. 
-->

```{css}
#| echo: false

@@

:::{.mx-auto .my-4 .img-45}
![](../figures/od-points.png)
:::

@@

:::{.w-50 .mx-auto .py-4}
| Type      | Weight | Approx. Speed     |
|:----------|--------|:------------------|
| primary   | 0.2    | 25 mph (41.5 kmh) | 
| secondary | 0.5    | 10 mph (16.2 kmh) |
| tertiary  | 0.8    | 07 mph (11.0 kmh) |

@@

:::{.mx-auto .my-4 .img-45}
![](../figures/cost-surface.png)
:::

@@

:::{.mx-auto .my-4 .img-65}
![](../figures/least-cost-paths.png)
:::

>>>>

```{=html}
<!-- 
RStudio/Quarto is having some issues with figure sizing, 
so using this hacky CSS solution. 
-->
```
```{css}
#| echo: false

@@

::: {.mx-auto .my-4 .img-45}
![](../figures/od-points.png)
:::

@@

::: {.w-50 .mx-auto .py-4}
| Type      | Weight | Approx. Speed     |
|:----------|--------|:------------------|
| primary   | 0.2    | 25 mph (41.5 kmh) |
| secondary | 0.5    | 10 mph (16.2 kmh) |
| tertiary  | 0.8    | 07 mph (11.0 kmh) |

@@

::: {.mx-auto .my-4 .img-45}
![](../figures/cost-surface.png)
:::

@@

::: {.mx-auto .my-4 .img-65}
![](../figures/least-cost-paths.png)
:::
